Consistency scores in text data

### 2020-07-08 outputs/documents/paper.Rmd
write up of GPT 3 WIP

OpenAI GPT-3 is

>>>>

### Article: Language Models are Few-Shot Learners (2020)
Official paper from OpenAI to introduce OpenAI GPT-3. Emphasizes on the "fewer-shots" and "task-agnostic" aspects of the latest langual model compared to its predecessor GPT-2.

In recent years, pre-trained language models have tremendous contributions in advancing a wide range of diverse natural language processing (NLP) tasks such as reading comprehension, text generation, and many others. The pre-trained models enables (citation). As the pre-trainde models remove the need for researchers and technologists to train models from scratch, they promote faster growth and advancement int he field of NLP. OpenAI GPT-3 is the latest generative pre-trained language model released by OpenAI in 2020. It has 175 billion parameters and is trained to [do that and that]. GPT-2, the predecessor of GPT-3, employs a semi-supervised approach that combines unsupervised pre-training and supervised fine-tuning where task-specific data set and task-specific fine-tuning were still needed in achieving these tasks until the birth of GPT-3 (citation). GPT-3 removes such needs, and its task-agnostic nature enables the accessible creation of cutting-edge NLP applications.

GPT-3 learns like human do — with brief directive and simple instruction...

In our application, we deploy OpenAI GPT-3 to generate text and ...
